Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-18 mu/article/article.tex
Changing subfigures.

\section{Introduction}
\blindtext
\begin{figure}[ht!]
    \centering
    \subfigure[\ $xz$ plane view]
    {\includegraphics[width=\linewidth]{figures/altstruc2}}
    \label{fig:alt-struc-xz}
    \\
    \subfigure[\ $xy$ plane view]
    {\includegraphics[width=\linewidth]{figures/altstruc1}}
    \label{fig:alt-struc-xy}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \subfigure[\ $xz$ plane view]
    {\includegraphics[width=\linewidth]{figures/upstruc2}}
    \label{fig:up-struc-xz}
    \\
    \subfigure[\ $xy$ plane view]
    {\includegraphics[width=\linewidth]{figures/upstruc1}}
    \label{fig:up-struc-xy}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\blindtext
\blindtext

@@

{\Large  We calculated the $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$} response In figure
\ref{fig:vab-str-comp} we present a comparison of the most intense responses
resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and \emph{up}
2D structures and CdSe and GaAs bulk systems. As we can see from this figure the
most intense response corresponds to the \emph{up} structure centered at
0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures. We found that the most intense response for the spin
velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
structure has a response more intense than the bulk systems but being less
intense than the corresponding to the \emph{up} one.
%

@@

\begin{figure}[t]
    \centering
    \subfigure[\ \label{fig:up-3d-vsz-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
    \\
    \subfigure[\ \label{fig:up-3d-vsz-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV and the local maximum from
    1.95\,eV to 2.0\,eV and both for polarization angles between $25^{\circ}$
    and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

@@

Eq. \eqref{eq:vab}. From the figure we have that the onset of the response
starts when the energy of the incoming beam is the same of the gap energy.

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for \emph{up}
    structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ for \emph{up}
    structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The absolute
    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

@@

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega,\alpha)$ and azimuthal $\varphi_{a}(\omega,\alpha)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and $\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The local maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy range from
    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}

@@

\textbf{Alt structure.}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}

@@

% %%%%%%%%%%%%%%%%
% %% Description of Up layer |V^{yz}|
% %%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ \label{fig:up-vyz-lay-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
    \\
    \subfigure[\ \label{fig:up-vyz-lay-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}

>>>>

\section{Introduction}
\blindtext
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \label{fig:alt-struc-xz}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \label{fig:alt-struc-xy}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \label{fig:up-struc-xz}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \label{fig:up-struc-xy}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\blindtext
\blindtext

@@

Using the Eq. \eqref{eq:vab}, we calculated the
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{alt} and
\emph{up} 2D structures and for the CdSe and GaAs bulk systems and the results
are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
From the figure we have that the onset of the response starts when the energy of
the incoming beam is the same of the gap energy.
% 
The most intense response corresponds to the \emph{up} structure centered at
0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures. We found that the most intense response for the spin
velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
structure has a response more intense than the bulk systems but being less
intense than the corresponding to the \emph{up} one.
%

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
    \label{fig:up-3d-vsz-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}
    \label{fig:up-3d-vsz-2}

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared, and the
    local maximum from 1.95\,eV to 2.0\,eV, in the visible, both for
    polarization angles between $25^{\circ}$ and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
     \label{fig:up-vaz-rag-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
     \label{fig:up-vaz-rag-2}

@@

Eq. \eqref{eq:vab}.

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
    \label{fig:up-3d-vvx-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
    \label{fig:up-3d-vvy-1}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The absolute
    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}

@@

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega,\alpha)$ and azimuthal $\varphi_{a}(\omega,\alpha)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and $\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
components.
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
    \label{fig:up-3d-vvx-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
    \label{fig:up-3d-vvy-2}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The local maxima
    of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 1.95\,eV to 2.00\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
    \label{fig:up-vx-comp-rtp-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
    \label{fig:up-vy-comp-rtp-2}

@@

\textbf{Alt structure.}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
    \label{fig:alt-3d-vvx}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
    \label{fig:alt-3d-vvy}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
    \label{fig:alt-vx-comp-rtp}
    \\
    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
    \label{fig:alt-vy-comp-rtp}

@@

% %%%%%%%%%%%%%%%%
% %% Description of Up layer |V^{yz}|
% %%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}
    \label{fig:up-vyz-lay-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}
    \label{fig:up-vyz-lay-2}
